% This file should be replaced with your file with an appendices (headings below are examples only)

% Placing of table of contents of the memory media here should be consulted with a supervisor
\chapter{Full list of Lumerical scripting language commands} \label{appendix:one}
\begin{itemize}
\item I - implemented
\item N - not implemented
\item O - out of scope
\item M - not supported by Meep
\item G - unnecessary, used for GUI
\end{itemize}

\begin{longtblr}[
  caption = {Long Title},
  label = {tab:commands},
]{
  colspec = {|XX[2]|},
  rowhead = 1,
  hlines,
  row{even} = {gray9},
  row{1} = {olive9},
} 
Lumerical command & Status \\
addrect  & Implemented \\
addcustom  & bar \\

abs\\
acos\\
add2dpoly\\
add2drect\\
add2visualizer\\
addabsorbing\\
addanalysisgroup\\
addanalysisprop\\
addanalysisresult\\
addassemblygroup\\
addattribute\\
addbandstructuremonitor\\
addbulkgen\\
addchargemesh\\
addchargemonitor\\
addchargesolver\\
addcircle\\
addconvectionbc\\
addctmaterialproperty\\
addcustom\\
adddeltachargesource\\
adddevice\\\
adddftmonitor\\
adddgtdmesh\\
adddgtdsolver\\
adddiffusion\\
adddipole\\
adddope\\
adddopinglayer\\
addeffectiveindex\\
addefieldmonitor\\
addelectricalcontact\\
addelement\\
addemabsorptionmonitor\\
addeme\\
addemeindex\\
addemeport\\
addemeprofile\\
addemfieldmonitor\\
addemfieldtimemonitor\\
addemmaterialproperty\\
addfde\\
addfdtd\\
addfeemmesh\\
addfeemsolver\\
addgaussian\\
addgridattribute\\
addgroup\\
addheatfluxbc\\
addheatfluxmonitor\\
addheatmesh\\
addheatsolver\\
addhtmaterialproperty\\
addimplant\\
addimport\\
addimportdope\\
addimportedsource\\
addimportgen\\
addimportheat\\
addimportnk\\
addimporttemperature\\
addindex\\
addjfluxmonitor\\
addjob\\
addlayer\\
addlayerbuilder\\
addmaterial\\
addmaterialproperties\\
addmesh\\
addmode\\
addmodeexpansion\\
addmodelmaterial\\
addmodesource\\
addmovie\\
addobject\\
addparameter\\
addpath\\
addpec\\
addperiodic\\
addplanarsolid\\
addplane\\
addpmc\\
addpml\\
addpoly\\
addport\\
addproperty\\
addpyramid\\
addradiationbc\\
addrcwa\\
addrect\\
addresource\\
addring\\
addsimulationregion\\
addsphere\\
addstructuregroup\\
addsurface\\
addsurfacechargebc\\
addsurfacerecombinationbc\\
addsweep\\
addsweepparameter\\
addsweepresult\\
addtemperaturebc\\
addtemperaturemonitor\\
addtfsf\\
addthermalinsulatingbc\\
addthermalpowerbc\\
addtime\\
addtogroup\\
addtolibrary\\
addtriangle\\
adduniformheat\\
adduserprop\\
addvarfdtd\\
addvoltagebc\\
addwaveguide\\
all\\
almostequal\\
amax\\
amin\\
analysis\\
and\\
angle\\
annotateproperty\\
any\\
arrayperiodicdata\\
asapexport\\
asapimport\\
asapload\\
asin\\
atan\\
atan2\\
atp\\
autoarrange\\
autosaveoff\\
autosaveon\\
\end{longtblr}


\chapter{Full implemented Lumerical grammar}\label{appendix:two}

\begin{longtblr}[\label{tab:full-grammar}
  caption = {Complete Grammar with Actions},
  label = {tab:full-commands}
]{
  colspec = {l|rcl}
}
 1. & \texttt{root}               & $\rightarrow$ & \emph{actions.Imports()} \emph{actions.StoreToBody()} \emph{actions.CreateSelector()} \emph{actions.StoreToBody()} \texttt{body} \\
 2. & \texttt{body}               & $\rightarrow$ & \texttt{statement} \emph{actions.StoreToBody()} \texttt{body} \\
 3. &                             & $|$           & \texttt{function} \texttt{body} \textbf{EOF} \\
 4. &                             & $|$           & $\varepsilon$ \\
 5. &                             & $|$           & \textbf{EOF} \\
 6. & \texttt{function}           & $\rightarrow$ & \textbf{FUNCTION} \textbf{IDENTIFIER} \textbf{(} \texttt{parameter\_list} \textbf{)} \textbf{\{} \texttt{nested\_body} \textbf{\}} \\
 7. & \texttt{nested\_body}       & $\rightarrow$ & \texttt{statement} \emph{actions.StoreToBody()} \texttt{nested\_body} \\
 8. &                             & $|$           & $\varepsilon$ \\
 9. & \texttt{nested\_else\_body} & $\rightarrow$ & \texttt{statement} \emph{actions.StoreToElse()} \texttt{nested\_else\_body} \\
10. &                             & $|$           & $\varepsilon$ \\
11. & \texttt{statement}          & $\rightarrow$ & \textbf{IDENTIFIER} \emph{actions.StoreVariableName()} \texttt{identifier\_action} \\
12. &                             & $|$           & \texttt{control\_structure} \\
13. &                             & $|$           & \texttt{selection} \\
14. &                             & $|$           & \textbf{?} \texttt{expression} \emph{actions.Print()} \textbf{;} \\
15. &                             & $|$           & \textbf{ADDFDTD} \emph{actions.AddFDTD()} \textbf{;} \\
16. &                             & $|$           & \textbf{ADDRECT} \emph{actions.AddRect()} \textbf{;} \\
17. &                             & $|$           & \textbf{ADDSPHERE} \emph{actions.AddSphere()} \textbf{;} \\
18. &                             & $|$           & \textbf{ADDPLANE} \emph{actions.AddPlaneSource()} \textbf{;} \\
19. &                             & $|$           & \textbf{ADDDFTMONITOR} \emph{actions.AddDFTMonitor()} \textbf{;} \\
20. &                             & $|$           & \textbf{SET} \textbf{(} \textbf{STRING} \emph{actions.StoreLiteral("str")} \texttt{expression} \emph{actions.SetProperty()} \textbf{)} \textbf{;} \\
21. &                             & $|$           & \textbf{BREAK} \emph{actions.Break()} \textbf{;} \\
22. & \texttt{selection}          & $\rightarrow$ & \textbf{SELECTALL} \emph{actions.SelectAll()} \textbf{;} \\
23. &                             & $|$           & \textbf{UNSELECTALL} \emph{actions.UnselectAll()} \textbf{;} \\
24. &                             & $|$           & \textbf{SELECT} \textbf{(} \textbf{STRING} \emph{actions.StoreLiteral("str")} \emph{actions.Select()} \textbf{)} \textbf{;} \\
25. &                             & $|$           & \textbf{SHIFTSELECT} \textbf{(} \textbf{STRING} \emph{actions.StoreLiteral("str")} \emph{actions.ShiftSelect()} \textbf{)} \textbf{;} \\
26. & \texttt{identifier\_action} & $\rightarrow$ & \texttt{assignment} \\
27. &                             & $|$           & \texttt{function\_call} \\
28. & \texttt{assignment}         & $\rightarrow$ & \textbf{=} \texttt{expression} \emph{actions.AssignToVariable()} \textbf{;} \\
29. & \texttt{function\_call}     & $\rightarrow$ & \textbf{(} \texttt{parameter\_list} \textbf{)} \textbf{;} \\
30. & \texttt{parameter\_list}    & $\rightarrow$ & \textbf{IDENTIFIER} \texttt{parameter\_list\_prime} \\
31. &                             & $|$           & $\varepsilon$ \\
32. & \texttt{parameter\_list\_prime} & $\rightarrow$ & \textbf{,} \textbf{IDENTIFIER} \texttt{parameter\_list\_prime} \\
33. &                             & $|$           & $\varepsilon$ \\
34. & \texttt{argument\_list}     & $\rightarrow$ & \texttt{expression} \texttt{argument\_list\_prime} \\
35. &                             & $|$           & $\varepsilon$ \\
36. & \texttt{argument\_list\_prime} & $\rightarrow$ & \textbf{,} \texttt{expression} \texttt{argument\_list\_prime} \\
37. &                             & $|$           & $\varepsilon$ \\
38. & \texttt{control\_structure} & $\rightarrow$ & \textbf{IF} \textbf{(} \texttt{expression} \textbf{)} \textbf{\{} \emph{actions.If()} \texttt{nested\_body} \textbf{\}} \texttt{elseNT} \\
39. &                             & $|$           & \textbf{FOR} \emph{actions.CreateEmptyWhile()} \textbf{(} \textbf{IDENTIFIER} \emph{actions.StoreVariableName()} \textbf{=} \texttt{expression} \emph{actions.AssignToVariable()} \texttt{loop\_condition} \textbf{)} \textbf{\{} \texttt{nested\_body} \emph{actions.HandleAllLoops()} \textbf{\}} \\
40. & \texttt{loop\_condition}     & $\rightarrow$ & \textbf{:} \texttt{expression} \emph{actions.CreateRangeCondition()} \texttt{range\_step} \\
41. &                             & $|$           & \textbf{;} \texttt{expression} \textbf{;} \texttt{expression} \emph{actions.CreateWhileCondition()} \\
42. & \texttt{range\_step}        & $\rightarrow$ & \textbf{:} \texttt{expression} \emph{actions.ExtendRangeCondition()} \\
43. &                             & $|$           & $\varepsilon$ \\
44. & \texttt{elseNT}             & $\rightarrow$ & \textbf{ELSE} \texttt{elifNT} \textbf{\{} \emph{actions.HandleElse()} \texttt{nested\_else\_body} \emph{actions.CleanUpElse()} \textbf{\}} \texttt{elseNT} \\
45. &                             & $|$           & $\varepsilon$ \\
46. & \texttt{elifNT}             & $\rightarrow$ & \textbf{IF} \textbf{(} \texttt{expression} \textbf{)} \\
47. &                             & $|$           & $\varepsilon$ \\
48. & \texttt{expression}         & $\rightarrow$ & \texttt{logic\_and} \\
49. & \texttt{logic\_and}         & $\rightarrow$ & \texttt{logic\_or} \texttt{logic\_and\_prime} \\
50. & \texttt{logic\_and\_prime}  & $\rightarrow$ & \textbf{AND} \texttt{equality} \emph{actions.LogicOperation(ast.And())} \texttt{logic\_and\_prime} \\
51. &                             & $|$           & $\varepsilon$ \\
52. & \texttt{logic\_or}          & $\rightarrow$ & \texttt{comparison} \texttt{logic\_or\_prime} \\
53. & \texttt{logic\_or\_prime}   & $\rightarrow$ & \textbf{OR} \texttt{equality} \emph{actions.LogicOperation(ast.Or())} \texttt{logic\_or\_prime} \\
54. &                             & $|$           & $\varepsilon$ \\
55. & \texttt{equality}           & $\rightarrow$ & \texttt{comparison} \texttt{equality\_prime} \\
56. & \texttt{equality\_prime}    & $\rightarrow$ & \textbf{!=} \texttt{comparison} \emph{actions.Comparison(ast.NotEq())} \texttt{equality\_prime} \\
57. &                             & $|$           & \textbf{==} \texttt{comparison} \emph{actions.Comparison(ast.Eq())} \texttt{equality\_prime} \\
58. &                             & $|$           & $\varepsilon$ \\
59. & \texttt{comparison}         & $\rightarrow$ & \texttt{term} \texttt{comparison\_prime} \\
60. & \texttt{comparison\_prime}  & $\rightarrow$ & \textbf{>} \texttt{term} \emph{actions.Comparison(ast.Gt())} \texttt{comparison\_prime} \\
61. &                             & $|$           & \textbf{>=} \texttt{term} \emph{actions.Comparison(ast.GtE())} \texttt{comparison\_prime} \\
62. &                             & $|$           & \textbf{<} \texttt{term} \emph{actions.Comparison(ast.Lt())} \texttt{comparison\_prime} \\
63. &                             & $|$           & \textbf{<=} \texttt{term} \emph{actions.Comparison(ast.LtE())} \texttt{comparison\_prime} \\
64. &                             & $|$           & $\varepsilon$ \\
65. & \texttt{term}               & $\rightarrow$ & \texttt{factor} \texttt{term\_prime} \\
66. & \texttt{term\_prime}        & $\rightarrow$ & \textbf{-} \texttt{factor} \emph{actions.BinaryOperation(ast.Sub())} \texttt{term\_prime} \\
67. &                             & $|$           & \textbf{+} \texttt{factor} \emph{actions.BinaryOperation(ast.Add())} \texttt{term\_prime} \\
68. &                             & $|$           & $\varepsilon$ \\
69. & \texttt{factor}             & $\rightarrow$ & \texttt{unary} \texttt{factor\_prime} \\
70. & \texttt{factor\_prime}      & $\rightarrow$ & \textbf{/} \texttt{unary} \emph{actions.BinaryOperation(ast.Div())} \texttt{factor\_prime} \\
71. &                             & $|$           & \textbf{*} \texttt{unary} \emph{actions.BinaryOperation(ast.Mult())} \texttt{factor\_prime} \\
72. &                             & $|$           & $\varepsilon$ \\
73. & \texttt{unary}              & $\rightarrow$ & \textbf{NOT} \texttt{unary} \\
74. &                             & $|$           & \textbf{-} \texttt{unary} \emph{actions.UnarySubtract()} \\
75. &                             & $|$           & \texttt{primary} \\
76. & \texttt{primary}            & $\rightarrow$ & \textbf{INTEGER} \emph{actions.StoreLiteral("int")} \\
77. &                             & $|$           & \textbf{FLOAT} \emph{actions.StoreLiteral("float")} \\
78. &                             & $|$           & \textbf{STRING} \emph{actions.StoreLiteral("str")} \\
79. &                             & $|$           & \textbf{IDENTIFIER} \emph{actions.StoreVariableName()} \\
80. &                             & $|$           & \textbf{(} \texttt{expression} \textbf{)} \\
\end{longtblr}
